
```{r}
library(tidyverse)
library(tidyr)
library(ggplot2)
library(ggcorrplot)
library(MASS)
library(splines)
library(readr)
library(leaps)
library(lmtest)
library(glmnet)
library(GGally)
library(tidymodels)
```
```{r}
bike <-
  read_csv("bike_cleaned-3.csv")

```

Which of the quantitative variables appears to be best correlated with "count"? #Temp
```{r}
ggcorr( bike, label = "TRUE", label_round =  2)
```


## Which "season" appears to have the highest count of rides?
```{r}
ggplot(bike,aes(x= count, y= season)) + geom_point(alpha=.1) + geom_smooth(method = "lm", color = "red") + theme_bw()
```

## Which statement best describes the general relationship between "temp" and "count"?  
```{r}
ggplot(bike,aes(x= temp, y= atemp)) + geom_point(alpha=.1) + geom_smooth(method = "lm", color = "red") + theme_bw()
```


# 7 What is the value of the slope coefficient for "hr23" in this model (to three decimal places)?

```{r}
ggplot(bike,aes(x= hr, )) + geom_point(alpha=.1) + geom_smooth(method = "lm", color = "red") + theme_bw()
```
```{r}
ggcorr( bike, label = "TRUE", label_round =  3)
```

```{r}
bike %>% group_by(season)%>% summarize(freq = )
```

```{r}
ggcorr( ames2, label = "TRUE", label_round =  2)
```
```{r}
ggpairs(, columns = c("GarageArea","GarageCars","1stFlrSF","TotalBsmtSF","OverallQual","SalePrice"))
ggpairs(ames2, columns = c("TotRmsAbvGrd", "GrLivArea","FullBath","YearRemodAdd","YearBuilt","SalePrice"))
```
# 1 bulid correlation mode: ignore "registered" "casual" "instant"
```{r}
bike2 <-  bike %>% dplyr::select("dteday","season","mnth","hr","holiday","weekday","workingday","weathersit","temp","atemp","hum","windspeed","count")
```

```{r}
glimpse(bike2)
```
#data exploration

```{r}
bike2 <- bike2 %>% mutate(season = as_factor(season))
```

```{r}
bike2 <- bike2 %>% mutate(hr = as_factor(hr))
```


```{r}
ggplot(bike2,aes(x = atemp)) + geom_histogram()+ theme_bw()
```

```{r}
ggcorr( bike2, label = "TRUE", label_round =  2)
```

# question 9 Create a linear regression model (using tidymodels as usual) with "temp" and "atemp" to predict "count". What is the adjusted R-squared value (to four decimal places) of this model?
```{r}
bike_recipe = recipe(count ~ temp + atemp, bike2)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit1 = fit(lm_wflow, bike2)
```

```{r}
summary(lm_fit1$fit$fit$fit)
```
# Question 6 Which statement best describes the general relationship between "temp" and "count"?  
```{r}
ggplot(bike2, aes(x = hr, y = count)) + geom_histogram() + theme_bw()
```

# Question 3 How many dummy (indicator) variables are used to represent "hr" in the model?
# question 7 What is the value of the slope coefficient for "hr23" in this model (to three decimal places)?
# Question 8 What is the adjusted R-squared value (to four decimal places) for the model from Question 7? 
```{r}
bike_recipe = recipe(count ~ hr, bike2) %>%
  step_dummy(all_nominal())

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit2 = fit(lm_wflow,bike2)


```

```{r}
summary(lm_fit2$fit$fit$fit)
```
# question 13 "stepwise Backward"

```{r}
allmod = lm(atemp ~., bike2)
summary(allmod)

emptymod = lm(temp ~ 1,bike2)
summary(emptymod)



```
# Question 13 The backward stepwise method removes only one variable. Which variable is removed? 
```{r} 
#backward
backmod = stepAIC(allmod, direction = "backward", trace = TRUE)
summary(backmod)
```
# Question 5 During which hour of the day does the model predict the highest number of rides?  
```{r}
mod2 = lm(hr~count,bike)
summary(mod2)

```

```{r}
bike2 %>% group_by(hr) %>% summarize(freq = n()) %>% arrange(desc(freq))
```
```{r}
table(bike2$hr)
```
```{r}
bike_recipe = recipe(count ~ hr, bike2)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit2 = fit(lm_wflow,bike2)
```

```{r}
summary(lm_fit2$fit$fit$fit)
```
```{r}
ggplot(bike,aes(x = hr, y = count) + geom_point())
```

```{r}
bike_recipe = recipe(count ~ hr, bike2)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit1 = fit(lm_wflow, bike2)
```

```{r}
summary(lm_fit2$fit$fit$fit)
```
```{r}
lm_fit2 %>% pull_workflow_fit() %>% tidy()
```

